\documentclass[letterpaper,12pt]{article}
\usepackage[section=3.6]{mathhw}
\usepackage{plotting}

\begin{document}

\maketitle

\begin{enumerate}
  \item[79.]
    The article ``Expectation Analysis of the Probability of Failure for Water Supply Pipes'' (\textit{J. of Pipeline Systems Engr. and Practice}, May 2012: 36–46) proposed using the Poisson distribution to model the number of failures in pipelines of various types. Suppose that for cast-iron pipe of a particular length, the expected number of failures is 1 (very close to one of the cases considered in the article). Then $X$, the number of failures, has a Poisson distribution with $\mu = 1$.
    \begin{enumerate}
      \item[a.]
        Obtain $P(X \le 5)$ by using Appendix Table A.2.
      \item[b.]
        Determine $P(X = 2)$ first from the pmf formula and then from Appendix Table A.2.
      \item[c.]
        Determine $P(2 \le X \le 4)$.
      \item[d.]
        What is the probability that $X$ exceeds its mean value by more than one standard deviation?
    \end{enumerate}
  \item[80.]
    Let $X$ be the number of material anomalies occurring in a particular region of an aircraft gas-turbine disk. The article ``Methodology for Probabilistic Life Prediction of Multiple-Anomaly Materials'' (\textit{Amer. Inst. of Aeronautics and Astronautics J.}, 2006: 787–793) proposes a Poisson distribution for $X$. Suppose that $\mu = 4$.
    \begin{enumerate}
      \item[a.]
        Compute both $P(X \le 4)$ and $P(X < 4)$.
      \item[b.]
        Compute $P(4 \le X \le 8)$.
      \item[c.]
        Compute $P(8 \le X)$.
      \item[d.]
        What is the probability that the number of anomalies exceeds its mean value by no more than one standard deviation?
    \end{enumerate}
  \item[82.]
    Consider writing onto a computer disk and then sending it through a certifier that counts the number of missing pulses. Suppose this number $X$ has a Poisson distribution with parameter $\mu = .2$. (Suggested in ``Average Sample Number for Semi-Curtailed Sampling Using the Poisson Distribution,'' \textit{J. Quality Technology}, 1983: 126–129.)
    \begin{enumerate}
      \item[a.]
        What is the probability that a disk has exactly one missing pulse?
      \item[b.]
        What is the probability that a disk has at least two missing pulses?
      \item[c.]
        If two disks are independently selected, what is the probability that neither contains a missing pulse?
    \end{enumerate}
  \item[84.]
    The Centers for Disease Control and Prevention reported in 2012 that 1 in 88 American children had been diagnosed with an autism spectrum disorder (ASD).
    \begin{enumerate}
      \item[a.]
        If a random sample of 200 American children is selected, what are the expected value and standard deviation of the number who have been diagnosed with ASD?
      \item[b.]
        Referring back to (a), calculate the approximate probability that at least 2 children in the sample have been diagnosed with ASD?
      \item[c.]
        If the sample size is 352, what is the approximate probability that fewer than 5 of the selected children have been diagnosed with ASD?
    \end{enumerate}
  \item[88.]
    In proof testing of circuit boards, the probability that any particular diode will fail is .01. Suppose a circuit board contains 200 diodes.
    \begin{enumerate}
      \item[a.]
        How many diodes would you expect to fail, and what is the standard deviation of the number that are expected to fail?
      \item[b.]
        What is the (approximate) probability that at least four diodes will fail on a randomly selected board?
      \item[c.]
        If five boards are shipped to a particular customer, how likely is it that at least four of them will work properly? (A board works properly only if all its diodes work.)
    \end{enumerate}
\end{enumerate}

\end{document}
