\documentclass[letterpaper,12pt]{article}
\usepackage[section=4.2]{mathhw}
\usepackage{physics}

\begin{document}

\maketitle

\begin{enumerate}
  \item[11.]
    Let $X$ denote the amount of time a book on two-hour reserve is actually checked out, and suppose the cdf is
    \begin{align*}
      F(x) = \begin{cases}
        0             & x < 0 \\
        \frac{x^2}{4} & 0 \le x < 2 \\
        1             & 2 \le x
      \end{cases}
    \end{align*}
    \begin{enumerate}
      \item[a.]
        Calculate $P(X \le 1)$.
        \begin{align*}
          P(X \le 1) = F(1) = \frac{1^2}{4} = \frac{1}{4}
        \end{align*}
      \item[b.]
        Calculate $P(.5 \le X \le 1)$.
        \begin{align*}
          P(.5 \le X \le 1) &= F(1) - F(.5) \\
          &= \frac{1^2}{4} - \frac{.5^2}{4} \\
          &= \frac{1}{4} - \frac{1}{16} \\
          &= \frac{3}{16}
        \end{align*}
      \item[c.]
        Calculate $P(X > 1.5)$.
        \begin{align*}
          P(X > 1.5) &= 1 - P(X \le 1.5) \\
          &= 1 - F(1.5) \\
          &= 1 - \frac{1.5^2}{4} \\
          &= 1 - \frac{9}{16} \\
          &= \frac{7}{16}
        \end{align*}
      \item[d.]
        What is the median checkout duration $\tilde{\mu}$? [solve $.5 = F(\tilde{\mu})$].
        \begin{align*}
          .5 &= F(\tilde{\mu}) = \frac{\tilde{\mu}^2}{4} \\
          2 &= \tilde{\mu}^2 \\
          \sqrt{2} &= \tilde{\mu}
        \end{align*}
      \item[e.]
        Obtain the density function $f(x)$.
        \begin{align*}
          f(x) &= F^\prime(x) \\
          &= \dv{x}(\frac{x^2}{4}) \\
          &= \frac{1}{4} \cdot \dv{x^2}{x} \\
          &= \frac{1}{4} \cdot 2x \\
          &= \frac{x}{2}
        \end{align*}
      \item[f.]
        Calculate $E(X)$.
        \begin{align*}
          E(X) &= \int_{0}^{2} x \cdot \frac{x}{2} \dd{x} \\
          &= \frac{1}{2} \int_{0}^{2} x^2 \dd{x} \\
          &= \frac{1}{2} \cdot \frac{x^3}{3} \bigg\rvert_{0}^{2} \\
          &= \frac{1}{6}(2^3 - 0^3) \\
          &= \frac{4}{3}
        \end{align*}
      \item[g.]
        Calculate $V(X)$ and $\sigma_X$.
        \begin{align*}
          E(X^2) &= \int_{0}^{2} x^2 \cdot \frac{x}{2} \dd{x} \\
          &= \frac{1}{2} \int_{0}^{2} x^3 \dd{x} \\
          &= \frac{1}{2} \cdot \frac{x^4}{4} \bigg\rvert_{0}^{2} \\
          &= \frac{1}{8}(2^4 - 0^3) \\
          &= 2 \\
          \\
          V(X) &= E(X^2) - [E(X)]^2 \\
          &= 2 - \left(\frac{4}{3}\right)^2 \\
          &= \frac{18}{9} - \frac{16}{9} \\
          &= \frac{2}{9} \\
          \\
          \sigma_X &= \sqrt{V(X)} = \sqrt{\frac{2}{9}} = \frac{\sqrt{2}}{3}
        \end{align*}
      \item[h.]
        If the borrower is charged an amount $h(X) = X^2$ when checkout duration is $X$, compute the expected charge $E[h(X)]$.
        \begin{align*}
          E(X^2) = 2
        \end{align*}
        Same as the calculation in (g).
    \end{enumerate}
  \item[12.]
    The cdf for $X$ (= measurement error) of Exercise 3 is
    \begin{align*}
      F(x) = \begin{cases}
        0                                                         & x < -2 \\
        \frac{1}{2} + \frac{3}{32}\left(4x - \frac{x^3}{3}\right) & -2 \le x < 2 \\
        1                                                         & 2 \le x
      \end{cases}
    \end{align*}
    \begin{enumerate}
      \item[a.]
        Calculate $P(X < 0)$.
      \item[b.]
        Calculate $P(-1 < X < 1)$.
      \item[c.]
        Calculate $P(.5 < X)$.
      \item[d.]
        Verify that $f(x)$ is as given in Exercise 3 by obtaining $F^\prime(x)$.
      \item[e.]
        Verify that $\tilde{\mu} = 0$.
    \end{enumerate}
  \item[13.]
    Example 4.5 introduced the concept of time headway in traffic flow and proposed a particular distribution for $X =$ the headway between two randomly selected consecutive cars (sec). Suppose that in a different traffic environment, the distribution of time headway has the form
    \begin{align*}
      f(x) = \begin{cases}
        \frac{k}{x^4} & x > 1 \\
        0             & x \le 1
      \end{cases}
    \end{align*}
    \begin{enumerate}
      \item[a.]
        Determine the value of $k$ for which $f(x)$ is a legitimate pdf.
      \item[b.]
        Obtain the cumulative distribution function.
      \item[c.]
        Use the cdf from (b) to determine the probability that headway exceeds 2 sec and also the probability that headway is between 2 and 3 sec.
      \item[d.]
        Obtain the mean value of headway and the standard deviation of headway.
      \item[e.]
        What is the probability that headway is within 1 standard deviation of the mean value?
    \end{enumerate}
  \item[15.]
    Let $X$ denote the amount of space occupied by an article placed in a 1-ft$^3$ packing container. The pdf of $X$ is
    \begin{align*}
      f(x) = \begin{cases}
        90x^8(1 - x) & 0 < x < 1 \\
        0            & \text{otherwise}
      \end{cases}
    \end{align*}
    \begin{enumerate}
      \item[a.]
        Graph the pdf. Then obtain the cdf of $X$ and graph it.
      \item[b.]
        What is $P(X \le .5)$ [i.e., $F(.5)$]?
      \item[c.]
        Using the cdf from (a), what is $P(.25 < X \le .5)$? What is $P(.25 \le X \le .5)$?
      \item[d.]
        What is the 75th percentile of the distribution?
      \item[e.]
        Compute $E(X)$ and $\sigma_X$.
      \item[f.]
        What is the probability that $X$ is more than 1 standard deviation from its mean value?
    \end{enumerate}
  \item[21.]
    An ecologist wishes to mark off a circular sampling region having radius 10 m. However, the radius of the resulting region is actually a random variable $R$ with pdf
    \begin{align*}
      f(r) = \begin{cases}
        \frac{3}{4}[1 - (10 - r)^2] & 9 \le r \le 11 \\
        0                           & \text{otherwise}
      \end{cases}
    \end{align*}
    What is the expected area of the resulting circular region?
\end{enumerate}

\end{document}
