\documentclass[letterpaper,12pt]{article}
\usepackage[section=4.4]{mathhw}
\usepackage{physics}

\begin{document}

\maketitle

\begin{enumerate}
  \item[59.]
    Let $X =$ the time between two successive arrivals at the drive-up window of a local bank. If $X$ has an exponential distribution with $\lambda = 1$ (which is identical to a standard gamma distribution with $\alpha = 1$), compute the following:
    \begin{enumerate}
      \item[a.]
        The expected time between two successive arrivals
        \begin{align*}
          \mu &= \frac{1}{\lambda} = 1
        \end{align*}
      \item[b.]
        The standard deviation of the time between successive arrivals
        \begin{align*}
          \sigma &= \frac{1}{\lambda} = 1
        \end{align*}
      \item[c.]
        $P(X \le 4)$
        \begin{align*}
          P(X \le 4) &= F(4; 1) \\
          &= 1 - e^{-1 \times 4} \\
          &= 1 - e^{-4} \\
          &\approx .981684
        \end{align*}
      \item[d.]
        $P(2 \le X \le 5)$
        \begin{align*}
          P(2 \le X \le 5) &= F(5; 1) - F(2; 1) \\
          &= (1 - e^{-1 \times 5}) - (1 - e^{-1 \times 2}) \\
          &= -e^{-5} + e^{-2} \\
          &\approx .128597
        \end{align*}
    \end{enumerate}
  \item[60.]
    Let $X$ denote the distance (m) that an animal moves from its birth site to the first territorial vacancy it encounters. Suppose that for banner-tailed kangaroo rats, $X$ has an exponential distribution with parameter $\lambda = .01386$ (as suggested in the article ``Competition and Dispersal from Multiple Nests,'' \textit{Ecology}, 1997: 873–883).
    \begin{enumerate}
      \item[a.]
        What is the probability that the distance is at most 100 m? At most 200 m? Between 100 and 200 m?
        \begin{align*}
          P(X \le 100) &= F(100; .01386) \\
          &= 1 - e^{-.01386 \times 100} \\
          &= 1 - e^{-1.386} \\
          &\approx .749926
        \end{align*}
        \begin{align*}
          P(X \le 200) &= F(200; .01386) \\
          &= 1 - e^{-.01386 \times 200} \\
          &= 1 - e^{-2.772} \\
          &\approx .937463
        \end{align*}
        \begin{align*}
          P(100 \le X \le 200) &= F(200; .01386) - F(100; .01386) \\
          &\approx .937463 - .749926 \\
          &\approx .187537
        \end{align*}
      \item[b.]
        What is the probability that distance exceeds the mean distance by more than 2 standard deviations?
        \begin{align*}
          \mu &= \sigma = \frac{1}{\lambda} = \frac{1}{.01386}
        \end{align*}
        \begin{align*}
          P(|X| > \mu + 2\sigma) &= 1 - P(|X| \le \mu + 2\sigma) \\
          &= 1 - P(X \le 3\mu) \\
          &= 1 - P\left(X \le \frac{1}{.01386} + \frac{2}{.01386}\right) \\
          &= 1 - P\left(X \le \frac{3}{.01386}\right) \\
          &= 1 - F\left(\frac{3}{.01386}; .01386\right) \\
          &= 1 - (1 - e^{\frac{-.01386 \times 3}{.01386}}) \\
          &= 1 - (1 - e^{-3}) \\
          &= e^{-3} \\
          &\approx .0497871
        \end{align*}
        $P(X \le \mu - 2\sigma)$ is discarded since $\mu > 0$, $F(x; \lambda) = 0$ for $x < 0$, and
        \begin{align*}
          x = \mu - 2\sigma = \mu - 2\mu = -\mu = < 0
        \end{align*}
      \item[c.]
        What is the value of the median distance?
        \begin{align*}
          F(x; .01386) &= \frac{1}{2} \\
          1 - e^{-.01386x} &= \frac{1}{2} \\
          \frac{1}{e^{.01386x}} &= \frac{1}{2} \\
          e^{.01386x} &= 2 \\
          .01386x &= ln(2) \\
          x &= \frac{ln(2)}{.01386} \\
          x &\approx 50.0106
        \end{align*}
        % \begin{align*}
        %   P(X \le m) &= .5 \\
        %   \int_{0}^{m} \lambda e^{-\lambda x} \dd{x} &= .5
        % \end{align*}
    \end{enumerate}
  \item[65.]
    Let $X$ denote the data transfer time (ms) in a grid computing system (the time required for data transfer between a ``worker'' computer and a ``master'' computer. Suppose that $X$ has a gamma distribution with mean value 37.5 ms and standard deviation 21.6 (suggested by the article ``Computation Time of Grid Computing with Data Transfer Times that Follow a Gamma Distribution,'' \textit{Proceedings of the First International Conference on Semantics, Knowledge, and Grid}, 2005).
    \begin{enumerate}
      \item[a.]
        What are the values of $\alpha$ and $\beta$?
      \item[b.]
        What is the probability that data transfer time exceeds 50 ms?
      \item[c.]
        What is the probability that data transfer time is between 50 and 75 ms?
    \end{enumerate}
  \item[67.]
    Suppose that when a transistor of a certain type is subjected to an accelerated life test, the lifetime $X$ (in weeks) has a gamma distribution with mean 24 weeks and standard deviation 12 weeks.
    \begin{enumerate}
      \item[a.]
        What is the probability that a transistor will last between 12 and 24 weeks?
      \item[b.]
        What is the probability that a transistor will last at most 24 weeks? Is the median of the lifetime distribution less than 24? Why or why not?
      \item[c.]
        What is the 99th percentile of the lifetime distribution?
      \item[d.]
        Suppose the test will actually be terminated after $t$ weeks. What value of $t$ is such that only .5\% of all transistors would still be operating at termination?
    \end{enumerate}
\end{enumerate}

\end{document}
